The Astropy Project

### 2017-10-17 main.tex
add frame transform graph figure

Many of the \texttt{Frame} classes also have attributes specific to the
corresponding reference system that allow the user to specify the frame.
For example, the Fifth Fundamental Catalogue (FK5) reference system requires
specifying an equinox to determine the reference frame.
If required, these additional frame attributes must be specified along with the
coordinate data when a \texttt{Frame} object is created.

@@

\begin{figure}
\includegraphics[width=\textwidth]{convolution_example.png}
An example showing different modes of convolution available in the \python ecosystem.  The red x's mark pixels that are set to NaN in the original data (a).  If the data are convolved with a Gaussian kernel on a 9x9 grid using scipy's direct convolution (b), any pixel within range of the original NaN pixels is also set to NaN.  Panel (c) shows what happens if the NaNs are set to zero first: the originally NaN regions are depressed relative to their surroundings.  Finally, panel (d) shows \astropypkg's convolution behavior, where the missing pixels are replaced with values interpolated from their surroundings using the convolution kernel.
\end{figure}

>>>>

Many of the \texttt{Frame} classes also have attributes specific to the
corresponding reference system that allow the user to specify the frame.
For example, the Fifth Fundamental Catalogue (FK5) reference system requires
specifying an equinox to determine the reference frame.
If required, these additional frame attributes must be specified along with the
coordinate data when a \texttt{Frame} object is created.
\figurename~\ref{fig:frame-transform-graph} shows the network of possible
reference frame transformations as currently implemented in
\texttt{astropy.coordinates}.
Custom, user-implemented \texttt{Frame} classes that define transformations to
any reference frame in this graph can then be transformed to any of the other
connected frames.

\begin{figure}
\includegraphics[width=\textwidth]{coordinates_graph.pdf}
The full graph of possible reference frame transformations implemented in
\texttt{astropy.coordinates}.
\label{fig:frame-transform-graph}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\textwidth]{convolution_example.png}
An example showing different modes of convolution available in the \python ecosystem.  The red x's mark pixels that are set to NaN in the original data (a).  If the data are convolved with a Gaussian kernel on a 9x9 grid using scipy's direct convolution (b), any pixel within range of the original NaN pixels is also set to NaN.  Panel (c) shows what happens if the NaNs are set to zero first: the originally NaN regions are depressed relative to their surroundings.  Finally, panel (d) shows \astropypkg's convolution behavior, where the missing pixels are replaced with values interpolated from their surroundings using the convolution kernel.
\label{fig:convolution-example}
\end{figure}
